% !TeX root = ../main.tex
\section{Synthesis}
\label{sec:synthesis}
\subsection{Decision analysis}
%explain TOPSIS and AHP
\noindent To make systematic and informed decisions for key aspects of the project, multi-criteria decision making (MCDM) methods were employed. Firstly, pairwise comparison of the criteria was performed with the Analytical Hierarchy Process (AHP) to produce criteria weightings which were fed into the Technique for Order of Preference by Similarity to Ideal Solution (TOPSIS) analysis. Processing of all relevant information though AHP and TOPSIS analysis yielded quantitative rankings for process alternatives, which were initially short-listed with qualitative arguments. Greater importance was given to safety and environmental concerns, technical performance and economic potential.
This methodology was applied to the following key choices: three products selection, plant location, toluene nitration synthesis, hydrogenation solvent and XXX 

\subsection{Product selection}
\noindent To deliver a multi-purpose plant, Nitroma selected toluene as feedstock due to the industrial importance of its nitration products and their amino derivatives. All three isomeric nitrotoluenes can indeed easily be oxidised and reduced to substituted aromatic amides of significant importance for the pharmaceutical, agrochemical and textile industries \cite{dugal_nitrobenzene_2005}. Six chemicals were initially selected due to their applications in drugs, fertilizers or dyes: 2-aminobenzaldehyde (precursor of quinoline derivatives for polymer, agrochemical, dye, antiviral and anti-malaria drug manufacturing), 4-aminobenzaldehyde (intermediate to pharmaceuticals and vanilin), 4-aminobenzoic acid (production of folic acid/vitamin B9), o-toluidine (intermediate in the manufacture of herbicides), m-toluidine (manufacture of  photographic color developer) and p-toluidine (for dye production) \cite{bowers_toluidines_2000,bruhne_benzaldehyde_2011,maki_benzoic_2000}. To determine the three most advantageous products to produce, AHP/TOPSIS analysis was conducted, giving significant importance to the safety of the compounds and their economic potential. Safety was assessed using the NFPA Hazard Classification for health, flammability and instability, where the smallest value is preferable. The economic potential of each chemical was determined using the average price, the average market share of producers which is an indicator of the market share Nitroma can plan to capture, the golbal demand and the expected market growth (CAGR). \Cref{tab:product} summarises the results and the complete methodology can be found in \Cref{app:matrix}.   


\begin{table}[h]
\centering
    \caption{AHP/TOPSIS results for product selection}
    \label{tab:product}\footnotesize
\begin{tabularx}{\linewidth}{l|S[table-format=4.2]S[table-format=1.1]XS[table-format=7.0,round-mode=figures,round-precision=2]|XX|lll|S[table-format=1.3]S[table-format=1.3]c}
\toprule
                                          & \multicolumn{4}{c}{Economic potential   (29\%)}                                & \multicolumn{2}{|>{\hsize=\dimexpr2\hsize+2\tabcolsep}X}{Process   complexity (14\%)} & \multicolumn{3}{|c|}{EHS (57\%)}     &                       &                          &                           \\ \cmidrule{2-10}
                                          & {\splitcell{Price\\(\si{\USD\per\kg})}} & {\splitcell{CAGR\\(\%)}} & \rcell{Average market share of producer (\%)} & {\splitcell{Demand\\(\si{\tonne\per\year})}} & \rcell{Number of reactions} & \rcell{Max selectivity to toluene (\%)} & \rotatebox[origin=r]{90}{Health} & \rotatebox[origin=r]{90}{Flammability} & \rotatebox[origin=r]{90}{Instability} & AHP & TOPSIS & Rank \\ \midrule
2-aminobenzaldehyde & 1711          & 5.6 & 0.77                           & 1344                 & 2                & 53                       & 2      & 1            & 1           & 0.124                 & 0.273                    & 6                         \\ 
4-aminobenzaldehyde & 19            & 7.1 & 1.75                           & 336842               & 2                 & 44                       & 2      & 1            & 0           & 0.188                 & 0.563                    & \cellcolor{green}2 \\ 
o-toluidine         & 5.8           & 7.8 & 0.88                           & 1327586              & 1                   & 53                       & 3      & 2            & 0           & 0.210                 & 0.611                    & \cellcolor{green}1 \\ 
p-toluidine         & 9             & 6.3 & 0.50                           & 722222               & 1                   & 44                       & 3      & 2            & 0           & 0.150                 & 0.333                    & 5                         \\ 
m-toluidine         & 8.9           & 8.2 & 0.57                           & 1067416              & 1                   & 3                       & 4      & 2            & 0           & 0.161                 & 0.458                    & 4                         \\ 
4-aminobenzoic acid & 26.29         & 5.8 & 3.70                           & 311906               & 2                 & 44                       & 2      & 1            & 1           & 0.168                 & 0.478                    & \cellcolor{green}3 \\ \bottomrule
\end{tabularx}
\end{table}

Due to their high economic potential and reduced health and fire hazards, 4-aminobenzaldehyde, o-toluidine and 4-aminobenzoic acid were found to be the most valuable compounds to be produced in Nitroma's multi-purpose plant.  A visual summary of the selected compounds and their associated synthesis pathways can be found in \Cref{app:matrix}.


\subsection{Nitration method}
\subsubsection{Choice of nitrating agent}
\noindent Nitric acid has been selected as the source of nitrogen for the nitration of toluene for its safe and environmentally friendly nature relative to other possible nitrating agents and its various favourable properties. \cite{miller_kinetics_1964, sreedhar_scientific_2013} Although nitric acid is a highly acidic and volatile compound, compared to alternatives such as acetone cyanohydrin and dinitrogen tetroxide which are highly toxic, nitric acid is more appropriate for industrial-scale nitration of toluene. \cite{dagade_nitration_2002, sreedhar_scientific_2013} Nitric acid, introduced as an aqueous solution, is the most commonly used and well-studied nitrating agent for this process in industry. \cite{bowers_toluidines_2000} A big advantage of aqueous nitric acid is that it can act as a self-catalyst by self-donating protons. \cite{miller_kinetics_1964} A common alternative to nitric acid is acetyl nitrate which is formed by the reaction of nitric acid with acetic anhydride. \cite{vassena_selective_1999} This reaction yields methanoic acid as by-product, resulting in a lower atom economy, and causes unnecessary difficulties in separations downstream by introducing more components into the process. The same argument can be employed for other alkyl nitrates such as butyl nitrate. To this end, nitric acid is deemed as the most suitable choice among all candidates.

\subsubsection{Choice of catalyst}
\noindent Nitration in industry is mainly carried out by a mixed-acid process, whereby sulfuric acid donates a proton to nitric acid, yielding a nitronium ion which will then react with toluene []. In addition to favouring less economically desirable $ortho$ isomers, product separation from the acid and acid regeneration are expensive and energy intensive \cite{sreedhar_scientific_2013}. These drawbacks can be overcome by using solid acid catalysts which offer an environmentally friendly and economic alternative to sulfuric acid \cite{vassena_selective_1999}. Based on those arguments, Nitroma will develop a safer and low environmental impact process employing zeolite catalysts for toluene nitration. More specifically, the relative benefits and disadvantages of 3 different zeolites were evaluated with the AHP and TOPSIS decision analysis methods to select the optimum catalyst. The economic potential, performance an safety of zeolites H-ZSM-5, H-Y and H-Mordenite were assessed and compared to the case with no catalyst \cite{jeeru_kinetics_2018}. The economic potential was measured with the cost of the catalyst and the percentage of undesirable by-product formed. Conversion and the NFPA score are the KPIs for performance and safety respectively. H-Mordenite was found optimum for the catalytic nitration of toluene by both AHP and TOPSIS analysis. The result table can be found in \Cref{app:matrix}. The kinetic model for the reaction was then developed and is presented in \Cref{app:kinetics}.

%assumptions
%catalyst selection process --> criteria + AHP/TOPSIS results


\subsection{Nitrotoluene Oxidation and hydrogenation pathways}
\subsubsection{o-toluidine production}
\noindent The $ortho$ isomer of nitrotoluene (53\%) is reduced to o-toluidine using  2\% w/w palladium-on-carbon (Pd/C) catalyst in the liquid-phase \cite{rajadhyaksha_solvent_1986}. This reaction is carried out in a solvent to dissolve solid reactants and products, absorb the heat of exothermic reaction and protect the catalyst surface from impurities. The chosen solvent can significantly affect the rate and selectivity of the hydrogenation []. Five different solvents, including methanol, propanol, butanol, cyclohexanol and hexane, were compared using AHP/TOPSIS analysis to determine the optimum solvent based on economic potential, performance, safety and environmental considerations. The performance of a solvent was measures through the activation energy of the reaction, the reaction rate at 333K and the solubility of \ch{H2} in the solvent \cite{rajadhyaksha_solvent_1986}. The financial KPI is solvent cost. Nitroma values this importance of using green solvents in its process and evaluated the sustainability of the different solvents using scores developed by GSK to assess the environmental impacts to produce the solvent, waste treatment and the fate and effects of the chemicals on the environment \cite{henderson_expanding_2011}. The GSK scored for health and flammability were also used. If a solvent could be sourced from renewable feed stocks, it was viewed positively \cite{byrne_tools_2016}. Both TOPSIS and AHP found that propanol was the most suitable green solvent for the reduction of 2-nitrotoluene. The table of scores is located in \Cref{app:matrix}.


%In all the above runs, the rates of reaction remained constant in each experiment for a conversion of more than 90\%, indicating zero-order dependence on the concentration of the nitro compound. The results indicate a 0.3 order dependence on hydrogen pressure or first order for pressure >280 kPa

\subsubsection{4-nitrotoluene oxidation}

\subsubsection{4-aminobenzoic acid synthesis}

\subsubsection{Preparation of 4-aminobenzaldehyde}

%assumptions
%catalyst/solvent/reductant/oxidant selection process --> criteria + AHP/TOPSIS results
%kinetics derivation

